Results

### 2019-09-10 analysis/03_analysis.Rmd
Commented out plotting for now

# Save plot
if (intercept == 1) file_name <- paste("intercept_marginal-posteriors.png")
if (public_affairs == 1) file_name <- paste("public-affairs_marginal-posteriors.png")
if (political_ideology == 1) file_name <- paste("political-ideology_marginal-posteriors.png")
if (social_views == 1) file_name <- paste("social-views_marginal-posteriors.png")
if (charity_voluntarism == 1) file_name <- paste("charity-voluntarism_marginal-posteriors.png")
if (demographics == 1) file_name <- paste("demographics_marginal-posteriors.png")
if (public_political == 1) file_name <- paste("public-political_marginal-posteriors.png")
if (public_political_social == 1) file_name <- paste("public-political-social_marginal-posteriors.png")
if (public_political_social_charity == 1) file_name <- paste("public-political-social-charity_marginal-posteriors.png")
if (public_political_social_charity_demo == 1) file_name <- paste("public-political-social-charity-demos_marginal-posteriors.png")
ggsave(
  file_name,
  path = here::here("analysis", "output", "figures"),
  width = ifelse(intercept == 1, 12, 20), 
  height = ifelse(sum(intercept, public_affairs, political_ideology, social_views, charity_voluntarism, demographics) == 1, 12, 20), 
  units = "in"
)
```

>>>>

# # Save plot
# if (intercept == 1) file_name <- paste("intercept_marginal-posteriors.png")
# if (public_affairs == 1) file_name <- paste("public-affairs_marginal-posteriors.png")
# if (political_ideology == 1) file_name <- paste("political-ideology_marginal-posteriors.png")
# if (social_views == 1) file_name <- paste("social-views_marginal-posteriors.png")
# if (charity_voluntarism == 1) file_name <- paste("charity-voluntarism_marginal-posteriors.png")
# if (demographics == 1) file_name <- paste("demographics_marginal-posteriors.png")
# if (public_political == 1) file_name <- paste("public-political_marginal-posteriors.png")
# if (public_political_social == 1) file_name <- paste("public-political-social_marginal-posteriors.png")
# if (public_political_social_charity == 1) file_name <- paste("public-political-social-charity_marginal-posteriors.png")
# if (public_political_social_charity_demo == 1) file_name <- paste("public-political-social-charity-demos_marginal-posteriors.png")
# ggsave(
#   file_name,
#   path = here::here("analysis", "output", "figures"),
#   width = ifelse(intercept == 1, 12, 20), 
#   height = ifelse(sum(intercept, public_affairs, political_ideology, social_views, charity_voluntarism, demographics) == 1, 12, 20), 
#   units = "in"
# )
```
